On $K_2$-analogue of Serre problem for $\SL_4$

### 2018-10-11 paper.tex
Added definition of precrpssed modules

\addbibresource{paper.bib}
\renewbibmacro*{volume+number+eid}{\ifentrytype{article}{\- \iffieldundef{volume}{}{Vol.~\printfield{volume},}\iffieldundef{number}{}{ No.~\printfield{number},}}}
\renewbibmacro{in:}{\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
\newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{http://dx.doi.org/\thefield{doi}}{#1}}}
\DeclareFieldFormat[article, inproceedings, inbook, book, thesis]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
\renewcommand*{\bibfont}{\footnotesize}
\DeclareMathOperator{\St}{St}
\DeclareMathOperator{\E}{E}
\DeclareMathOperator{\T}{T}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\Um}{Um}
\DeclareMathOperator{\colim}{colim}
\DeclareMathOperator{\GL}{GL}
\DeclareMathOperator{\SL}{SL}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\K}{K}
\DeclareMathOperator{\rk}{rk}
\DeclareMathOperator{\Sym}{Sym}
\newcommand{\catname}[1]{{\normalfont\textbf{#1}}}

@@

\subsection{Various stuff}
\[ T_{ij}(at^{-1}) = \sigma_i T_{ij}(a) \sigma_i^{-1} = \sigma_j^{-1} T_{ij}(a) \sigma_j \]
\[ [[x_{ij}(a t^{-1}), x_{jk}(b t^{-1})],  x_{kl}(c)] = [x_{ik}(a b t^{-1}),  x_{kl}(c t^{-1})] \]
\[ \sigma_i [[x_{ij}(a), x_{jk}(b t^{-1})],  x_{kl}(c)] \sigma_i^{-1} =  \sigma_i [x_{ik}(a b),  x_{kl}(c t^{-1})] \sigma_i^{-1} \]
\begin{multline}
[[x_{ij}(at^{-1}), x_{jk}(bt^{-1})], x_{jl}(ct^{-1})] = \sigma_i [[ x_{ij}(a), x_{jk}(bt^{-1})], x_{jl}(ct^{-1})] \sigma_i^{-1} = \\
\sigma_i \sigma_k^{-1} \sigma_l^{-1} [[ x_{ij}(a), x_{jk}(b)], x_{jl}(c)] \sigma_l \sigma_k \sigma_i^{-1} = 1
\end{multline}
\[ [b, c] =1,\ [a^c, b] = c^{-1} a c b c^{-1} a^{-1} c b^{-1} =  c^{-1} a b  a^{-1} b^{-1} c = [a, b]^c \]

We need to prove that $\sigma_i$ commute with $x_{jk}(a)$ if $j\neq i, k \neq i$.

@@

\begin{dfn} {\it Tulenbaev's cube} is a collection of abstract groups and morphisms between them which make the diagram below commute.
\[\xymatrix{
G_{123} \ar[rr]_{f_{23}} \ar[dd]_{f_{12}} \ar[rd]_{f_{13}} &                        & G_{23} \ar[dd]^(.3){g_2^3} \ar[rd]^{g^2_3} &           \\
                                & G_{13} \ar[rr]^(.3){g^1_3} \ar^(.3){g^3_1}[dd] &                   & G_3 \ar[dd]_{h_3} \\
G_{12} \ar[rr]^(.3){g_2^1} \ar[rd]_{g_1^2}          &                        & G_2 \ar[rd]_{h_2}         &           \\
                                & G_1 \ar[rr]_{h_1}              &                   & G}\]
In addition, we require these maps to satisfy the following list of axioms:
\begin{enumerate}
 \item $G_1$ acts on $G_{13}$, $G$ acts on $G_3$ %??? vertical arrows $G_{13} \to G_1$ and $G_3 \to G$ are crossed modules
 \item for every $b \in G_{13}$ and $x \in G_1$ one has $g_1^3(b ^ x) = x^{-1} \cdot g_1^3(b) \cdot x$; (precrossed)
 \item for every $x\in G_{13}$, $b \in G_{13}$ one has $g_3^1(b^x) = g_3^1(b)^{h_1(x)}$; ($g_3^1$ map of precrossed modules?)
 %\item $g_3^1(b)^{h_1g_2^1(a)} = g_3^1(b^{g_1^2(a)})$
 \item for every $z_1, z_2 \in G_3$ one has $z_1^{-1} z_2 z_1 = z_2^{h_3(z_1)}$ (Peiffer)
\end{enumerate}
\end{dfn}
Now set $V = G_1 \times G_2 \times G_3$, $W = G_{12} \times G_{13} \times G_{23}$.
We define an operation $- \star - \colon W \times V \to V$ as follows. For $v = (x, y, z) \in V$ and $(a, b, c) \in W$ we set 
\[(a, b, c) \star (x, y, z) = (x \cdot g_1^3(b) \cdot g_1^2(a),\ g_2^1(a)^{-1} \cdot y \cdot g_2^3(c),\ g_3^2(c)^{-1} \cdot g_3^1(b)^{-h_2(y)} \cdot z)\]

@@

@@

Denote by $V_0$ the set $\St(\Phi, A[t]) \times \StH(A[t, t^{-1}]) \times \St(\Phi, A[t, t^{-1}], m[t, t^{-1}])$. 
We define an equivalence relation $\sim$ on $V_0$ as the minimal equivalence relation generated by the following 4 elementary transformations:
\begin{enumerate}
 \item $(a \cdot u, b, \beta) \sim (a, j_+^*(u) \cdot b, \beta)$, where $u$ is an element $\UU(\Phi^+, A[t])$;
 \item $(a \cdot \ext{m[t]}(\gamma), b, \beta) \sim (a, b, j^*_+(\gamma)^b \cdot \beta)$, where $\gamma$ is an element of $\St(\Phi, A[t], m[t])$;
 \item $(a, b \cdot u, \beta) \sim (a, b, u\cdot \beta)$, where $u$ is an element of $\UU(\Phi^+, m[t, t^{-1}])$;
 \item $(a, b \cdot \{ t, a \}_\alpha, \beta) \sim (a, b, \{ t, a \}'_\alpha \cdot \beta) $, where $a \in (1+m)^*$
  and $\{t, a\}'_\alpha$ is a relative Steinberg symbol discussed in~\cref{sec:relative-steinberg}
\end{enumerate}

>>>>

\addbibresource{paper.bib}
\renewbibmacro*{volume+number+eid}{\ifentrytype{article}{\- \iffieldundef{volume}{}{Vol.~\printfield{volume},}\iffieldundef{number}{}{ No.~\printfield{number},}}}
\renewbibmacro{in:}{\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
\newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{http://dx.doi.org/\thefield{doi}}{#1}}}
\DeclareFieldFormat[article, inproceedings, inbook, book, thesis]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
\renewcommand*{\bibfont}{\footnotesize}
\DeclareMathOperator{\St}{St}
\DeclareMathOperator{\E}{E}
\DeclareMathOperator{\T}{T}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\Um}{Um}
\DeclareMathOperator{\colim}{colim}
\DeclareMathOperator{\GL}{GL}
\DeclareMathOperator{\SL}{SL}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\K}{K}
\DeclareMathOperator{\rk}{rk}
\DeclareMathOperator{\Sym}{Sym}
\DeclareMathOperator{\Ker}{Ker}
\newcommand{\catname}[1]{{\normalfont\textbf{#1}}}

@@

Let us recall some basic terminology pertaining to crossed modules (cf.~\cite[\S~3.3]{BHS11}). Let $M$ and $N$ be groups, of which $N$ acts on $M$ on the right. By definition, a {\it precrossed module} is a group morphism $\mu \colon M \to N$ such that $\mu(m^n) = \mu(m)^n = n^{-1} \cdot \mu(m) \cdot n$. A precrossed module is called a {\it crossed module} if additionally Peiffer identity is satisfied, i.\,e. for $m, m'\in M$ one has $m^{-1} m' m = {m'}^{\mu(m)}$.
A morphism between (pre)crossed modules $\mu \colon M \to N$ and $\mu'\colon M \to N$ is a pair $(f, g)$ of group morphisms $f\colon M \to M'$, $g \colon N \to N'$ such that the diagram 
\begin{equation} \xymatrix{ M \ar[r]^{\mu} \ar[d]_{f} & N \ar[d]^{g} \\ M' \ar[r]^{\mu'} & N'}\end{equation} commutes and moreover $f(m^n) = f(m)^{g(n)}$.

\subsection{Factorizations of Steinberg groups}

\begin{lemma}\label{lem:bruhat}
Let $\Phi$ be any irreducible root system.
Let $\Phi^+$, $\Phi^{+'}$ be two systems of positive roots in $\Phi$.
 \begin{lemlist}
\item  The Steinberg group
$\St(\Phi,A)$ admits the following analogue of the Bruhat decomposition:
\begin{equation}\label{eq:bruhat}
\St(\Phi,A) =\bigsqcup_{w\in W(\Phi)} \left(\UU(\Phi^{+'}, A)\cdot wH(\Phi,A)\cdot\UU(\Phi^+, A) \cdot
\ker\bigl(\St(\Phi,A) \xrightarrow{\pi^*} \St(\Phi,k)\bigr)\right).
\end{equation}
\item Assume that $uwhvl=u'w'h'v'l'$ for some $u,u'\in \UU(\Phi^{+'}, A)$, $w,w'\in W(\Phi)$,
$h,h'\in H(\Phi,A)$, and $l,l'\in \Ker\bigl(\St(\Phi,A) \xrightarrow{\pi^*} \St(\Phi,k)\bigr)$. Then
$w=w'$,
$$
h^{-1}h'\in \Sym(\Phi,A)\cdot\ker\bigl(H(\Phi,A) \xrightarrow{\pi^*} H(\Phi,k)\bigr),
$$
and
there exist $a\in \UU(\Phi^{+'},m)$ such that $w^{-1}(u^{-1}u'a)w\in \UU(\Phi^+,R)$,
and $b\in\UU(\Phi^+,m)$ such that
$$
b=v^{-1}(u^{-1}u')^{wh}v'=l(l')^{-1}.
$$
 \end{lemlist}
\end{lemma}

%TODO: Formulate Gauss decomposition

\begin{comment}
\subsection{Various stuff}
\[ T_{ij}(at^{-1}) = \sigma_i T_{ij}(a) \sigma_i^{-1} = \sigma_j^{-1} T_{ij}(a) \sigma_j \]
\[ [[x_{ij}(a t^{-1}), x_{jk}(b t^{-1})],  x_{kl}(c)] = [x_{ik}(a b t^{-1}),  x_{kl}(c t^{-1})] \]
\[ \sigma_i [[x_{ij}(a), x_{jk}(b t^{-1})],  x_{kl}(c)] \sigma_i^{-1} =  \sigma_i [x_{ik}(a b),  x_{kl}(c t^{-1})] \sigma_i^{-1} \]
\begin{multline}
[[x_{ij}(at^{-1}), x_{jk}(bt^{-1})], x_{jl}(ct^{-1})] = \sigma_i [[ x_{ij}(a), x_{jk}(bt^{-1})], x_{jl}(ct^{-1})] \sigma_i^{-1} = \\
\sigma_i \sigma_k^{-1} \sigma_l^{-1} [[ x_{ij}(a), x_{jk}(b)], x_{jl}(c)] \sigma_l \sigma_k \sigma_i^{-1} = 1
\end{multline}
\[ [b, c] =1,\ [a^c, b] = c^{-1} a c b c^{-1} a^{-1} c b^{-1} =  c^{-1} a b  a^{-1} b^{-1} c = [a, b]^c \]

We need to prove that $\sigma_i$ commute with $x_{jk}(a)$ if $j\neq i, k \neq i$.
\end{comment}

@@

\begin{dfn} {\it Tulenbaev's cube} is a collection of abstract groups and morphisms between them which make the diagram below commute.
\[\xymatrix{
G_{123} \ar[rr]_{f_{23}} \ar[dd]_{f_{12}} \ar[rd]_{f_{13}} &                        & G_{23} \ar[dd]^(.3){g_2^3} \ar[rd]^{g^2_3} &           \\
                                & G_{13} \ar[rr]^(.3){g^1_3} \ar^(.3){g^3_1}[dd] &                   & G_3 \ar[dd]_{h_3} \\
G_{12} \ar[rr]^(.3){g_2^1} \ar[rd]_{g_1^2}          &                        & G_2 \ar[rd]_{h_2}         &           \\
                                & G_1 \ar[rr]_{h_1}              &                   & G}\]
In addition, we require these maps to satisfy the following list of axioms:
\begin{enumerate}
 \item $G_1$ acts on $G_{13}$, $G$ acts on $G_3$ %??? vertical arrows $G_{13} \to G_1$ and $G_3 \to G$ are crossed modules
 \item for every $b \in G_{13}$ and $x \in G_1$ one has $g_1^3(b ^ x) = x^{-1} \cdot g_1^3(b) \cdot x$; (precrossed)
 \item for every $x\in G_{13}$, $b \in G_{13}$ one has $g_3^1(b^x) = g_3^1(b)^{h_1(x)}$; ($g_3^1$ map of precrossed modules?)
 %\item $g_3^1(b)^{h_1g_2^1(a)} = g_3^1(b^{g_1^2(a)})$
 \item for every $z_1, z_2 \in G_3$ one has $z_1^{-1} z_2 z_1 = z_2^{h_3(z_1)}$ (Peiffer)
\end{enumerate}
\end{dfn}
Now set $V = G_1 \times G_2 \times G_3$, $W = G_{12} \times G_{13} \times G_{23}$.
We define an operation $- \star - \colon W \times V \to V$ as follows. For $v = (x, y, z) \in V$ and $(a, b, c) \in W$ we set 
\[(a, b, c) \star (x, y, z) = (x \cdot g_1^3(b) \cdot g_1^2(a),\ g_2^1(a)^{-1} \cdot y \cdot g_2^3(c),\ g_3^2(c)^{-1} \cdot g_3^1(b)^{-h_2(y)} \cdot z).\]

@@

\begin{lemma}
 Then the kernel of $h_3\colon G_3\to G_1$ is generated by $g_3^1(\Ker(g_1^3))$.
\end{lemma}

@@

\begin{comment}                                
Denote by $V_0$ the set $\St(\Phi, A[t]) \times \StH(A[t, t^{-1}]) \times \St(\Phi, A[t, t^{-1}], m[t, t^{-1}])$. 
We define an equivalence relation $\sim$ on $V_0$ as the minimal equivalence relation generated by the following 4 elementary transformations:
\begin{enumerate}
 \item $(a \cdot u, b, \beta) \sim (a, j_+^*(u) \cdot b, \beta)$, where $u$ is an element $\UU(\Phi^+, A[t])$;
 \item $(a \cdot \ext{m[t]}(\gamma), b, \beta) \sim (a, b, j^*_+(\gamma)^b \cdot \beta)$, where $\gamma$ is an element of $\St(\Phi, A[t], m[t])$;
 \item $(a, b \cdot u, \beta) \sim (a, b, u\cdot \beta)$, where $u$ is an element of $\UU(\Phi^+, m[t, t^{-1}])$;
 \item $(a, b \cdot \{ t, a \}_\alpha, \beta) \sim (a, b, \{ t, a \}'_\alpha \cdot \beta) $, where $a \in (1+m)^*$
  and $\{t, a\}'_\alpha$ is a relative Steinberg symbol discussed in~\cref{sec:relative-steinberg}
\end{enumerate}
\end{comment}
